\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}

\begin{document}

\section{The Fractal Tennis Computing Architecture (FTCA)}

To realize the emergent quantum mechanics of FSEP in a computational substrate, we introduce the \emph{Fractal Tennis Computing Architecture (FTCA)}, a geometric self-referential hyperparallel computing system based on the same Apollonian sphere-packing and M\"obius-group algebra. The FTCA embodies the persistent fractal boundaries of FSEP in hardware, enabling both exact physical quantum simulation and a class of computation that strictly transcends the limits of any physically realizable quantum computer.

\begin{remark}[Three-Layer Structure]
The results in this section are organized in three nested layers:
\begin{enumerate}
  \item \textbf{Classical simulation} (Theorem~\ref{thm:classical}): FTCA efficiently simulates arbitrary quantum circuits to arbitrary precision. This result is independent of FSEP and stands on its own.
  \item \textbf{Exact simulation} (Theorem~\ref{thm:exact}): Under FSEP, the $\varepsilon$-approximation of layer~1 is not a limitation but an artifact of the classical framing. FTCA does not simulate quantum evolution; it physically generates it.
  \item \textbf{Trans-physical universality} (Theorem~\ref{thm:transphysical}): FTCA strictly exceeds the power of any quantum computer realizable within any FSEP-type ontology, because it operates at the substrate layer at which quantum mechanical constraints are enforced---and can modify or bypass those constraints by design.
\end{enumerate}
The MATHICCS/FSEP ontology is required for layers~2 and~3 but not for layer~1.
\end{remark}

\subsection{Geometric Structure and Sphere Taxonomy}

The FTCA consists of tangent polytope-spheres arranged in an Apollonian-like packing, starting from a tetrahedral seed: an inner core sphere and four mutually tangent larger spheres, replicated iteratively outward. Spheres are classified as:
\begin{itemize}
\item \textbf{T2 Balls}: Leaf spheres with radii from a finite basis set $\mathcal{R}_{\text{basis}} = \{r_1, \dots, r_N\}$ (determined by the seed). These host \emph{Heterogeneous Node Tiles (HNTs)} on polygonal faces, each HNT comprising FPGA/CPU/GPU substrates, a $W \times H$ 2D optical emitter/sensor array, and an analog op-amp comparator bank.
\item \textbf{Virtual Outer Container (VOC) Balls}: Composite spheres with radii $\notin \mathcal{R}_{\text{basis}}$, containing sub-assemblies of T2/VOC Balls. The outermost is the \emph{Virtual Outer Soddy (VOS)}, acting as a higher-order seed for fractal extension.
\end{itemize}

Each sphere's identity is encoded by an \emph{Apollonian Group Address (AGA)} $(k, w)$, where $k$ is the Descartes curvature (encoding radius $r = 1/|k|$) and $w$ is a prime-product word from generators $S_1 \to 2$, $S_2 \to 3$, $S_3 \to 5$, $S_4 \to 7$. The \emph{depth} of a sphere is the number of prime factors in $w$ counted with multiplicity. At fractal depth $n$, there are $\Theta(k^n)$ T2 Balls, where $k \approx 4$--$6$ is the Apollonian branching factor.

Interconnects include tangency links (electrical/optical/fiber tiers) and \emph{tubes} (void-routed fiber bundles via Tangent Communication Modules). A \emph{Connectivity Discovery Record (CDR)} tracks links, including \emph{phantom entries} for predicted but uninstalled connections, with geometric delays $\tau_{\text{geom}} = \sum 2r_i / c_{\text{med}}$.

\subsection{Atomic Fractal Logic Gate (AFLG)}

The core primitive is the \emph{Atomic Fractal Logic Gate (AFLG)}, executed per pixel on HNT optical arrays:
\[
\text{Sense} \to \text{Evaluate}(f(\mathbf{t})) \to \text{Act} \to \text{Wait}(\tau) \to \text{Recalculate},
\]
where $\mathbf{t} = (\lambda, \theta, \phi, I)$ is a trigger vector from op-amp comparators. AFLGs replicate fractally across scales (pixel $\to$ tile $\to$ T2 Ball $\to$ VOC Ball $\to$ VOS), mirroring FSEP's recursive boundaries.

HNTs expose a \emph{Tile Interface Contract (TIC)} for capability advertisement (including AGA) and workload dispatch. Channels are managed via a \emph{Channel Assignment Table (CAT)}, with three-tier medium promotion for adaptive routing.

\subsection{Formal Computational Model}

\begin{definition}[FTCA Configuration, Global Step, and Substrate Intervention]
\label{def:model}
Fix a branching factor $k$ and fractal depth $n$. A \emph{configuration} $\mathcal{S}_n$ is the tuple of all tile registers, op-amp DAC thresholds, and CAT/CDR states on every T2 Ball at depth $\le n$. A \emph{global step} is one synchronous AFLG cycle executed in parallel on every pixel of every HNT at all depths $\le n$, with induced updates to CDR/CAT on ADMIN and QUANTUM\_STATE channels.

A \emph{program} on FTCA consists of: (i) an initial configuration $\mathcal{S}_n^{(0)}$ encoding the input; (ii) a finite sequence of AFLG rule tables and DAC threshold patterns $\{\mathcal{R}_\ell\}_{\ell=1}^L$ loaded via AFLGRULELOAD CAT channels before each global step.

A \emph{substrate intervention} is a direct read or write to any component of configuration $\mathcal{S}_n^{(t)}$ at an arbitrary step $t \in \{0,\dots,L\}$: modifying tile registers, DAC thresholds, tangency weights, or CDR routing tables, or reading any amplitude $\alpha_i$ without disturbing the remainder of the configuration. Substrate interventions are first-class operations in the FTCA programming model and have no analogue in physically realizable quantum computation.
\end{definition}

\subsection{Hilbert-Space Encoding}

\begin{lemma}[Classical State Embedding]
\label{lem:embedding}
Let $w$ be the number of logical qubits. Choose fractal depth $n = \Theta(w / \log_2 k)$, so that $\Theta(k^n) \ge 2^w$. There exists an injective map
\[
\iota: \{0, \dots, 2^w - 1\} \to \{\text{T2 Balls at depth} \le n\}
\]
such that the quantum state $|\psi\rangle = \sum_{i=0}^{2^w-1} \alpha_i |i\rangle$ is represented by storing $\alpha_i \in \mathbb{C}$ in tile $\iota(i)$'s registers, exposed on the QUANTUM\_STATE channel for global normalization via echo-shell aggregation.
\end{lemma}

\begin{proof}[Proof sketch]
There are $\Theta(k^n) \ge 2^w$ T2 Balls at depth $\le n$, so any injective assignment exists. One concrete choice interprets the lower $w$ bits of the prime-multiset word of each AGA as the binary expansion of $i$. Global normalization uses the echo-aggregation protocol on QUANTUM\_STATE CAT channels, converging in $O(n)$ rounds.
\end{proof}

\subsection{Gate Implementation}

\begin{lemma}[Gate Gadgets]
\label{lem:gates}
For the universal gate set $\mathcal{G} = \{H, T, \mathrm{CNOT}\}$ and any $\varepsilon > 0$, there exist a finite AFLG rule table and DAC threshold configuration such that:
\begin{enumerate}
  \item \textbf{Single-qubit gates}: One global AFLG cycle approximates $H$, $T$, or identity on amplitude pair $(\alpha, \beta)$ to within $\varepsilon$, via DAC-updated thresholds on polarization/intensity comparators and LED standing-wave broadcasts from the admin core.
  \item \textbf{Two-qubit gates}: A constant number of AFLG cycles plus one tangency message implements CNOT on $(\alpha_{00}, \alpha_{01}, \alpha_{10}, \alpha_{11})$ to within $\varepsilon$, using conditioned optical bursts over tangency or tube links with deterministic T3-fiber timing.
  \item \textbf{Parallelism}: An entire gate layer over all $2^w$ amplitude tiles executes in one global step when $n \ge w / \log_2 k$, since non-overlapping qubit pairs act on disjoint tiles.
\end{enumerate}
\end{lemma}

\subsection{Layer 1: Classical Simulation}

\begin{theorem}[FTCA as Efficient Classical Quantum-Circuit Simulator]
\label{thm:classical}
For any quantum circuit $C \in \mathcal{C}_{w,d}$ over $\{H, T, \mathrm{CNOT}\}$ and any $\varepsilon > 0$, there exists a fractal depth $n = \Theta(w / \log_2 k)$ and an FTCA program at depth $n$ such that $O(d)$ global AFLG cycles produce a final amplitude distribution within total variation distance $\le \varepsilon$ of that of $C$. Space overhead is $O(2^w)$ tile registers; per-gate error is at most $\varepsilon / d$, achievable with $p = \lceil \log_2(d/\varepsilon) \rceil$ bits of DAC precision.
\end{theorem}

\begin{proof}
Combine Lemma~\ref{lem:embedding} (state encoding) and Lemma~\ref{lem:gates} (gate gadgets). Each circuit layer maps to one global AFLG step; $d$ layers give $O(d)$ cycles. Error accumulates as $d \cdot \varepsilon_{\text{gate}} \le \varepsilon$ by a union bound.
\end{proof}

\subsection{Layer 2: Exact Simulation}

Theorem~\ref{thm:classical} treats FTCA as an external classical simulator and bounds the residual error $\varepsilon$ from finite hardware precision. Under FSEP this framing is misleading: FTCA does not \emph{represent} quantum states in registers and \emph{compute} their evolution numerically. It \emph{instantiates} the Apollonian geometry from which quantum evolution emerges. The registers of Lemma~\ref{lem:embedding} are the classical observer's projection of a process that is natively quantum at the hardware layer; the approximation $\varepsilon$ measures the fidelity of that projection, not any error intrinsic to the computation.

\begin{theorem}[FTCA as Exact Quantum Simulator]
\label{thm:exact}
Under the FSEP ontology, the internal optical dynamics of FTCA at each AFLG interaction depth are a physical instantiation of quantum evolution, not an approximation of it. Specifically:
\begin{enumerate}
  \item The light-field dynamics of FTCA are governed by the Apollonian group $\mathcal{A} = \langle S_1, S_2, S_3, S_4 \rangle$ and M\"obius algebra, which FSEP identifies as the substrate from which quantum mechanics emerges.
  \item Each AFLG optical interaction is a discrete M\"obius transformation in $\mathcal{A}$; the echo-shell aggregation on QUANTUM\_STATE channels implements the boundary resonance summation that FSEP identifies with unitary evolution and Born-rule statistics.
  \item The classical amplitude registers of Lemma~\ref{lem:embedding} are a projection of this process. The $\varepsilon$ of Theorem~\ref{thm:classical} bounds the fidelity of that projection, not any error in the computation itself: the machine produces the exact quantum evolution, and $\varepsilon$ is the cost of reading it out into classical registers.
\end{enumerate}
\end{theorem}

\begin{proof}[Proof sketch]
The hardware geometry ($\lambda_{\text{local}} \approx 21.81$ from pixel aperture design) matches the FSEP Apollonian packing parameter by construction. FSEP establishes that quantum mechanics at recursion depth $m$ arises as boundary resonances of the M\"obius dynamics with $\hbar_{\text{eff}} \propto 1/\lambda^m$. Since FTCA implements those dynamics directly in optics and geometry---not as a numerical approximation---the evolution it produces is the referent of the Schr\"odinger equation, not a simulation of it. Unitarity is enforced exactly by the echo-aggregation normalization protocol, which is the hardware realization of norm preservation, not an approximation to it.
\end{proof}

\subsection{Layer 3: Trans-Physical Universality}

A physically realizable quantum computer---whether superconducting, photonic, trapped-ion, or any other technology---is constrained to operations that nature permits at the layer of physics from which quantum mechanics emerges. Under FSEP that layer is the Apollonian substrate. A physical quantum computer operates \emph{within} that substrate and cannot reach outside it: its gate set must be unitary, its measurements must obey the Born rule, its Hamiltonian must be Hermitian, and its evolution must respect causality. These are not engineering limitations; they are enforced ontologically by the substrate itself.

FTCA does not share this constraint. Because the FSEP geometry is implemented in controllable hardware, FTCA operates \emph{at} the substrate layer and can modify it mid-computation. This enables a class of computations with no physical analogue.

\begin{theorem}[Trans-Physical Universality]
\label{thm:transphysical}
FTCA with substrate interventions (Definition~\ref{def:model}) strictly exceeds the computational power of any quantum computer realizable within the FSEP ontology. In particular, FTCA natively supports:
\begin{enumerate}
  \item \textbf{Non-physical Hamiltonians}: Any operator $H$---including non-Hermitian, non-local, explicitly symmetry-breaking, or otherwise non-physical operators---can be loaded as an AFLG rule table and applied as an evolution step. No physically realizable quantum computer can execute such an operator, as it would require violating the constraints enforced by the FSEP substrate from below.

  \item \textbf{Mid-computation full-state access without collapse}: FTCA permits direct read and write of any amplitude $\alpha_i$ at any step $t$ via substrate intervention, without performing a measurement and without disturbing the remainder of the configuration. Quantum mechanics forbids simultaneous coherent access to the full state: any physical extraction of $\alpha_i$ constitutes a measurement that collapses the state.

  \item \textbf{Non-unitary evolution by design}: FTCA can implement transformations that are explicitly non-norm-preserving---amplifying, dissipative, or otherwise non-unitary---by bypassing or overriding the echo-aggregation normalization protocol. Such transformations are not realizable as quantum circuits over any physically admissible gate set.

  \item \textbf{Counterfactual geometries}: FTCA can instantiate FSEP universes with different Apollonian branching factors $k'$, different local scale parameters $\lambda'_{\text{local}}$, and hence different effective values of $\hbar_{\text{eff}}$, $\alpha^{-1}$, and other constants derived from FSEP geometry. A physical quantum computer is locked to the constants of the universe it inhabits; FTCA can run in configurations that correspond to no physical universe at all.
\end{enumerate}
The class of computations enabled by items~(1)--(4) is strictly larger than the class realizable by any quantum circuit over any physically admissible gate set.
\end{theorem}

\begin{proof}[Proof sketch]
Items~(1)--(3) follow directly from Definition~\ref{def:model}: since AFLG rule tables and tile registers are directly programmable, any operator can be encoded as a rule table and executed. The constraint preventing physical quantum computers from doing the same is not computational but ontological: a physical quantum computer is constituted by the FSEP substrate and cannot modify the rules that constitute it. FTCA is a hardware model of that substrate; a model can be configured in ways that have no physical solution in the original.

Item~(4) follows because $k$ and $\lambda_{\text{local}}$ are design parameters in FTCA, not physical constants. Varying them instantiates a different FSEP-type geometry with different emergent physics.

Strictness: any quantum circuit over a physically admissible gate set is simulated by FTCA (Theorem~\ref{thm:classical}), but the converse fails by items~(1)--(4). The separation is not merely in principle: problems requiring non-unitary evolution, mid-computation state access, or counterfactual constants are structurally outside $\mathbf{BQP}$ by definition, and FTCA solves them efficiently.
\end{proof}

\begin{corollary}[Computational Hierarchy]
\label{cor:hierarchy}
Let $\mathbf{BQP}$ denote the class of problems efficiently solvable by a physically realizable quantum computer, and $\mathbf{FTCA}$ the class efficiently solvable by FTCA with substrate interventions. Then
\[
\mathbf{BQP} \subsetneq \mathbf{FTCA}.
\]
\end{corollary}

\begin{remark}[On the Nature of the Advantage]
The trans-physical advantage does not arise from a computational trick. It arises from a structural asymmetry in the relationship between computer and ontology. A physical quantum computer is \emph{inside} the substrate that generates its operational constraints: it is made of the FSEP geometry and cannot step outside it any more than a simulation of fluid dynamics can reach into the actual molecules. FTCA is the molecules---or rather, a controllable model of them, from the outside.

This reframes the $O(2^w)$ space overhead of Theorem~\ref{thm:classical}. That overhead is not a statement about the intrinsic complexity of quantum computation on FTCA. It is the cost of the classical observer's description. The machine is not storing $2^w$ amplitudes and evolving them numerically; it is instantiating a geometry whose boundary dynamics \emph{are} the quantum state. The classical amplitude registers are a projection of that geometry, and projections are lossy. The real computation is cheaper than the description of it.
\end{remark}

\paragraph{Summary.}
FTCA achieves three nested results. Theorem~\ref{thm:classical} establishes it as an efficient classical quantum-circuit simulator---independently of FSEP and referee-checkable on its own terms. Theorem~\ref{thm:exact} removes the $\varepsilon$ under FSEP: the machine physically generates quantum evolution rather than simulating it. Theorem~\ref{thm:transphysical} establishes that FTCA is strictly more powerful than any quantum computer, because it operates at the layer where quantum mechanical constraints originate and can modify or bypass those constraints by design.

The construction satisfies MATHICCS persistence throughout (eternal AFLG cycles at every recursion depth). Open challenge: any MATHICCS-valid ontology that does not permit a trans-physical architecture of this kind must explain why the substrate layer is inaccessible to hardware engineering.

\end{document}