% =====================================================================
% CLASSP: Continuum Limit of Apollonian-Soddy Sphere Packing Dynamics
% Corrected merged draft --- May 2026
% =====================================================================
\documentclass[11pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{array}
\usepackage{enumitem}
\usepackage{mdframed}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{conjecture}{Conjecture}
\newtheorem{assumption}{Assumption}
\newtheorem{corollary}{Corollary}

\newcommand{\ASSP}{\mathrm{ASSP}}
\newcommand{\FTC}{\mathrm{FTC}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\kpc}{\mathrm{kpc}}
\newcommand{\kly}{\mathrm{kly}}
\newcommand{\R}{\mathbb{R}}

\title{CLASSP: The Continuum Limit of Apollonian--Soddy\
Sphere Packing Dynamics as the Origin of Weak-Field\
Gravity and Dirac Quantum Mechanics}
\author{Steven E.\ Elliott}
\date{May 2026}

\begin{document}
\maketitle

\begin{abstract}
The companion paper~\cite{TFOFT2026} establishes the ontology: the universe
is fundamentally a finite operational computational object defined by a
dynamical Apollonian--Soddy Sphere Packing (ASSP) fractal quine operating
under Presburger arithmetic~\cite{Presburger1929}. In that picture, continuum
field theories are not fundamental; they are bounded-resolution effective
descriptions of finite tangency updates. This paper develops the first
continuum-limit equations of the ASSP program. We define a tangency graph
whose vertices are spheres, whose edges are tangencies, and whose primitive
local clock variable is the sphere radius. Writing $u_i=\ln(R_i/R_0)$, we
show that the radius-clock equation $\Delta_G u_i=(4\pi G/c^2)\rho_i$
coarse-grains to the Newtonian Poisson equation and to the weak-field time
component of general relativity. We then construct an Ord-type~\cite{Ord1983}
directed tangency walk on the same graph: light-speed propagation plus a local
Gyro-Ball chirality-mixing angle $\theta_i=mc^2\Delta\tau_i/\hbar$
coarse-grains to the Dirac equation on the radius-clock metric. We further
state a candidate Maxwell limit from U(1) edge-phase holonomies. Thus GR and
QM are not fundamental competitors; they are complementary continuum shadows
of the same finite ASSP update. Finally, we translate the TFOFT $3d_{z^2}$
Milky Way claim into a corrected simulation and observational program. Using
the real Fermi-bubble scale, $H_{\rm FB}\sim10$--$15\,\kpc$ rather than
$50\,\kpc$, the associated equatorial ``Fermi donut'' should peak in the
outer visible disk at $R\sim10$--$15\,\kpc$, with a fiducial inner shoulder
near $R\sim0.8H_{\rm FB}\sim8$--$12\,\kpc$, and with one-quarter the
polar-lobe angular density contrast. This places the test in the same radial
regime where Gaia DR3 studies report declining or model-sensitive rotation
curves and where a dark-matter-disk model has been reported to fit some
large-radius on/off-plane behavior better than a canonical NFW halo.
\end{abstract}

\tableofcontents
\newpage

% ===================================================================
\section{Motivation}
% ===================================================================

The original TFOFT paper~\cite{TFOFT2026} proposes MATHICCS: every
mathematical operation in a physical law must correspond to a persistently
realizable physical procedure. Completed infinities, exact real continua, and
singular points are therefore not ontological primitives. They may remain
useful approximations, but only as coarse-grained descriptions of finite
physical computation.

The candidate finite ontology is the dynamical Apollonian--Soddy Sphere
Packing~\cite{Soddy1936,Boyd1973,Graham2003}. Primitive objects are not fields
on a continuum, but spheres, curvatures, tangencies, and local update rules. A
single sphere stores a state; two tangent spheres form the minimal
law-generating unit, the Gyro Ball. Across fractal scales, the same object is
conjectured to appear as electron/nucleus at atomic scale and star/core at
galactic scale. Flat galactic rotation curves~\cite{Sofue2012,Chemin2009} and
atomic orbital quantization are then interpreted as opposite-side projections
of one fractal boundary dynamics.

This paper asks a narrow technical question:
\begin{quote}
If the ASSP ontology of~\cite{TFOFT2026} is correct, what continuum field
equations appear when a bounded-resolution observer coarse-grains the finite
tangency dynamics?
\end{quote}
The answer developed here is that the two dominant continuum theories emerge
from complementary limits of the same graph:
\begin{align*}
\text{radius-clock scalar }u=\ln(R/R_0)
  &\;\longrightarrow\; \text{Newtonian gravity and weak-field }g_{00},\\
\text{directed tangency walk with Gyro mixing}
  &\;\longrightarrow\; \text{Dirac quantum matter},\\
\text{U(1) edge-phase holonomies}
  &\;\longrightarrow\; \text{candidate Maxwell/gauge field limit}.
\end{align*}
The target is not to quantize general relativity. Under TFOFT, that target is
category-mistaken: GR and QM are already effective views of the same finite
fractal update, observed from different sides of the boundary.

% ===================================================================
\section{The ASSP Tangency Graph}
% ===================================================================

\subsection{Graph structure}

Let the sphere packing define a graph $G=(V,E)$, where each vertex $i\in V$
is a sphere with center $x_i\in\R^3$, radius $R_i>0$, and curvature
$b_i=1/R_i$. An edge is a tangency:
\begin{equation}
  (i,j)\in E \iff |x_i-x_j|=R_i+R_j.
  \label{eq:tangency}
\end{equation}
The edge vector and length are
\begin{equation}
  s_{ij}=x_j-x_i,\qquad \ell_{ij}=|s_{ij}|=R_i+R_j.
  \label{eq:edge}
\end{equation}
The packing is recursively determined by the Descartes--Soddy curvature
relation~\cite{Soddy1936,Graham2003}:
\begin{equation}
  k_5=\sum_{i=1}^{4}k_i\pm2\sqrt{\sum_{i<j}k_i k_j},\qquad k_i=R_i^{-1}.
  \label{eq:soddy}
\end{equation}

\subsection{Radius as local time}

The defining physical identification is
\begin{equation}
  u_i=\ln\frac{R_i}{R_0},
  \label{eq:u_def}
\end{equation}
where $R_0$ is the reference radius. In the Presburger-minimal TFOFT basis one
takes $R_0=\pi$~\cite{TFOFT2026}, but the continuum-limit derivations below do
not depend on that choice. The local clock rate is
\begin{equation}
  \dd\tau_i=e^{u_i}\dd t=\frac{R_i}{R_0}\dd t.
  \label{eq:clock}
\end{equation}
A bounded-resolution observer describes this through the emergent metric
\begin{equation}
  \dd s^2=-c^2e^{2u(x)}\dd t^2+\dd\ell_G^2,
  \label{eq:metric}
\end{equation}
where $\dd\ell_G^2$ is the spatial metric induced by the packing. In the GR
weak field, $\dd\tau\approx(1+\Phi/c^2)\dd t$; comparing with
$\dd\tau=e^u\dd t\approx(1+u)\dd t$ gives
\begin{equation}
  \Phi=c^2u=c^2\ln\frac{R}{R_0}.
  \label{eq:phi_u}
\end{equation}
\emph{Gravity is the coarse-grained logarithmic gradient of the ASSP
radius-clock field.}

\subsection{Normalized graph Laplacian}

For a field $f_i=f(x_i)$ slowly varying across the graph, define the weighted
graph Laplacian
\begin{equation}
  (\Delta_G f)_i=A_i\sum_{j\sim i}w_{ij}(f_j-f_i),
  \label{eq:lap_general}
\end{equation}
with symmetric tangency conductances $w_{ij}=w_{ji}>0$. A natural
radius-symmetric choice is
\begin{equation}
  w_{ij}=\frac{4\pi}{R_i+R_j}\left(\frac{R_iR_j}{R_i+R_j}\right)^2,
  \label{eq:weights}
\end{equation}
though the continuum proof below requires only local symmetry and finite
second moments. Define
\begin{equation}
  M_i^{ab}=\sum_{j\sim i}w_{ij}s_{ij}^a s_{ij}^b,\qquad
  M_i=\sum_{j\sim i}w_{ij}|s_{ij}|^2.
  \label{eq:moments}
\end{equation}
We assume local coarse-grained balance and isotropy:
\begin{align}
  \sum_{j\sim i}w_{ij}s_{ij}^a&=0,
  \label{eq:balance}\\
  M_i^{ab}&=\frac{M_i}{3}\delta^{ab}.
  \label{eq:isotropy}
\end{align}
Condition~\eqref{eq:balance} holds in idealized ASSP interiors by packing
symmetry; condition~\eqref{eq:isotropy} holds statistically under local
coarse-graining over an ASSP cluster~\cite{Mandelbrot1983,Boyd1973}. Choose
$A_i=6/M_i$, giving
\begin{equation}
  (\Delta_G f)_i
  =\frac{6}{\displaystyle\sum_{j\sim i}w_{ij}|s_{ij}|^2}
    \sum_{j\sim i}w_{ij}(f_j-f_i).
  \label{eq:normalized_lap}
\end{equation}

% ===================================================================
\section{Weak-Field Gravity as the Radius-Clock Continuum Limit}
% ===================================================================

\subsection{Coarse-graining theorem}

\begin{theorem}[Laplacian limit]
\label{thm:laplacian}
Let $f_i=f(x_i)$ with $f$ smooth on scales large compared to the local sphere
spacing $h_i\sim R_i$. Under conditions~\eqref{eq:balance}--\eqref{eq:isotropy},
\begin{equation}
  (\Delta_G f)_i=\nabla^2f(x_i)+O(h_i|\nabla^3f|).
  \label{eq:lap_limit}
\end{equation}
\end{theorem}

\begin{proof}
Taylor-expand $f_j=f(x_i+s_{ij})$:
\begin{equation}
  f_j-f_i=s_{ij}^a\partial_a f+	frac12s_{ij}^as_{ij}^b\partial_a\partial_bf
  +O(|s_{ij}|^3\nabla^3f).
  \label{eq:taylor}
\end{equation}
Substitute into~\eqref{eq:lap_general}. The first-order term vanishes
by~\eqref{eq:balance}. The leading contribution is
\begin{align}
  (\Delta_G f)_i
  &=\frac{A_i}{2}\sum_{j\sim i}w_{ij}s_{ij}^as_{ij}^b\partial_a\partial_bf
     +O(h_i|\nabla^3f|) \nonumber\\
  &=\frac{A_i}{2}\cdot\frac{M_i}{3}\delta^{ab}\partial_a\partial_bf
     +O(h_i|\nabla^3f|). \nonumber
\end{align}
Using $A_i=6/M_i$ gives $(\Delta_G f)_i=\nabla^2f+O(h_i|\nabla^3f|)$.
\end{proof}

\subsection{Poisson equation and Newtonian gravity}

Postulate the ASSP radius-clock source equation
\begin{equation}
  \Delta_Gu_i=\frac{4\pi G}{c^2}\rho_i.
  \label{eq:discrete_poisson}
\end{equation}
By Theorem~\ref{thm:laplacian}, the continuum limit is
$\nabla^2u=(4\pi G/c^2)\rho$. Multiplying by $c^2$ and using
$\Phi=c^2u$ from~\eqref{eq:phi_u}:
\begin{equation}
  \boxed{\nabla^2\Phi=4\pi G\rho.}
  \label{eq:poisson}
\end{equation}
The slow-particle geodesic acceleration follows from metric~\eqref{eq:metric}:
\begin{equation}
  \vec a=-\frac{c^2}{2}\nabla\ln\!\left(-\frac{g_{00}}{c^2}\right)
  =-c^2\nabla u=-\nabla\Phi.
  \label{eq:acceleration}
\end{equation}
For a spherical mass $M$, $\Phi(r)=-GM/r$, giving
\begin{equation}
  R(r)=R_0\exp\!\left(-\frac{GM}{c^2r}\right)
  \approx R_0\!\left(1-\frac{GM}{c^2r}\right),
  \label{eq:R_point}
\end{equation}
so local radius, local clock rate, and local coordinate light speed decrease
in a potential well.

\subsection{Weak-field GR slot}

From $\Phi=c^2u$ and metric~\eqref{eq:metric}:
\begin{equation}
  g_{00}=-c^2e^{2\Phi/c^2}
  \approx -c^2\!\left(1+\frac{2\Phi}{c^2}\right),
  \label{eq:g00_weak}
\end{equation}
which is the weak-field GR time component. The ASSP radius-clock scalar $u$
is the pre-continuum object whose smooth limit is the gravitational potential
and whose weak-field metric form is the $g_{00}$ sector of GR. This paper does
not claim to derive the full Einstein tensor; the spatial metric sector and
strong-field limit require a separate CLASSP treatment.

\subsection{M\"obius boundary acceleration generator}

At a tangency point the M\"obius boundary map is conjectured to generate the
exact acceleration
\begin{equation}
  a_M(r)=\frac{2v^2}{r}\!\left(1+\frac{r_s}{r}\right)^{-2}
       =\frac{2v^2r}{(r+r_s)^2},\qquad
  r_s=\frac{2GM}{c^2},
  \label{eq:mobius_accel}
\end{equation}
whose Laurent expansion is
\begin{equation}
  a_M(r)=\frac{2v^2}{r}-\frac{4v^2r_s}{r^2}
  +\frac{6v^2r_s^2}{r^3}-\frac{8v^2r_s^3}{r^4}+O(r_s^4/r^5).
  \label{eq:laurent}
\end{equation}
The successive radial powers match the hierarchy normally associated with
flat-rotation support ($1/r$), Newtonian gravity ($1/r^2$), GR perihelion
precession ($1/r^3$), and frame-dragging-order corrections ($1/r^4$). The
coefficients and exact observational normalization remain part of the CLASSP
strong-field/disk-dynamics program.

\subsection{Dynamic radius field equation}

The dynamical ASSP radius equation is taken to be
\begin{equation}
  \frac{1}{c^2}\ddot u_i-(\Delta_Gu)_i=\frac{4\pi G}{c^2}\rho_i,
  \label{eq:wave_gravity}
\end{equation}
whose continuum limit is the scalar wave equation
\begin{equation}
  \Box u=\frac{4\pi G}{c^2}\rho,\qquad
  \Box=-\frac{1}{c^2}\partial_t^2+\nabla^2.
  \label{eq:scalar_wave}
\end{equation}
Gravitational radiation corresponds, at this level, to propagating
perturbations of $u$. The tensorial sector is expected to arise from the
coarse-grained dynamics of $\dd\ell_G^2$.

% ===================================================================
\section{Dirac Quantum Mechanics as the Directed-Tangency Continuum Limit}
% ===================================================================

\subsection{One-dimensional Ord walk on a tangency chain}

The minimal case follows Ord~\cite{Ord1983} but on the ASSP tangency graph
rather than an externally imposed lattice. Use two directed amplitudes
$\psi_R(x,t)$ and $\psi_L(x,t)$ for right- and left-moving tangency states.
Let the local step length be $\epsilon$ and the local proper tick be
$\Delta\tau=\epsilon/c$. Mass enters as a local Gyro-Ball chirality-mixing
angle:
\begin{equation}
  \theta=\frac{mc^2\Delta\tau}{\hbar}.
  \label{eq:theta}
\end{equation}
The discrete update rule is
\begin{align}
  \psi_R(x+\epsilon,t+\Delta\tau)
    &=\cos\theta\,\psi_R(x,t)-i\sin\theta\,\psi_L(x,t),
  \label{eq:walk_R}\\
  \psi_L(x-\epsilon,t+\Delta\tau)
    &=\cos\theta\,\psi_L(x,t)-i\sin\theta\,\psi_R(x,t).
  \label{eq:walk_L}
\end{align}
For $\theta\ll1$ and slowly varying amplitudes, Taylor-expanding
Eqs.~\eqref{eq:walk_R}--\eqref{eq:walk_L} and using $\epsilon/\Delta\tau=c$
and $\theta/\Delta\tau=mc^2/\hbar$ gives
\begin{align}
  (\partial_t+c\partial_x)\psi_R&=-i\frac{mc^2}{\hbar}\psi_L,
  \label{eq:chiral_R}\\
  (\partial_t-c\partial_x)\psi_L&=-i\frac{mc^2}{\hbar}\psi_R.
  \label{eq:chiral_L}
\end{align}
Writing $\Psi=(\psi_R,\psi_L)^T$, Eqs.~\eqref{eq:chiral_R}--\eqref{eq:chiral_L}
become
\begin{equation}
  \boxed{i\hbar\partial_t\Psi=-i\hbar c\,\sigma_z\partial_x\Psi+mc^2\sigma_x\Psi.}
  \label{eq:dirac_1d}
\end{equation}
This is the $1+1$-dimensional Dirac equation~\cite{Dirac1928}.

\subsection{Radius-clock insertion}

On the ASSP graph the local proper tick is set by the local sphere radius:
\begin{equation}
  \Delta\tau_i\sim\frac{2R_i}{c}.
  \label{eq:tick_radius}
\end{equation}
The mixing angle therefore becomes
\begin{equation}
  \theta_i=\frac{mc^2\Delta\tau_i}{\hbar}
  \sim\frac{2mcR_i}{\hbar}=\frac{2R_i}{\lambda_C},
  \qquad \lambda_C=\frac{\hbar}{mc},
  \label{eq:theta_radius}
\end{equation}
and mass is the chirality-reversal rate per local sphere-clock tick:
\begin{equation}
  \boxed{m=\frac{\hbar}{c^2}\frac{\theta_i}{\Delta\tau_i}.}
  \label{eq:mass_flip}
\end{equation}
Massless modes ($\theta=0$) stream without flip. Massive modes undergo
repeated reversals, producing the fractal zigzag path that Ord~\cite{Ord1983}
showed generates quantum behavior after coarse-graining.

\subsection{Three-dimensional ASSP walk and curved-space Dirac limit}

Assign spinor amplitudes to oriented tangency edges:
\begin{equation}
  \psi_{i\to j}^A(t),
  \label{eq:spinor_edge}
\end{equation}
where $A$ is a spin/channel index. The local update is
\begin{equation}
  \psi_{i\to j}^A(t+\Delta t_i)
  =\sum_{k\sim i}S_i{}^A{}_B(j,k)\,\psi_{k\to i}^B(t),
  \label{eq:assp_walk}
\end{equation}
where the Gyro-Ball scattering matrix satisfies $S_i^\dagger S_i=I$. Under
local balance and isotropy of tangency directions,
\begin{equation}
  \langle n^a\rangle_i=0,\qquad
  \langle n^a n^b\rangle_i=\tfrac13\delta^{ab},
  \label{eq:spinor_moments}
\end{equation}
the continuum expansion of~\eqref{eq:assp_walk} gives the Dirac equation on
the radius-clock metric:
\begin{equation}
  \boxed{
  i\hbar\gamma^\mu e_\mu{}^a
  \!\left(\partial_a+\Omega_a+\frac{iq}{\hbar}A_a\right)\!\Psi
  -mc\,\Psi=0.}
  \label{eq:dirac_curved}
\end{equation}
Here $e_\mu{}^a$ is the tetrad of metric~\eqref{eq:metric}, with time
component $e_0{}^0=e^{-u}=R_0/R$; the spin connection $\Omega_a$ is the
continuum limit of inter-sphere frame rotations; and $A_a$ arises from U(1)
tangency edge phases. Thus the same graph that produces gravity through its
radius-clock field produces quantum matter through its directed spinor walk.

% ===================================================================
\section{Candidate Electromagnetic Limit from Edge-Phase Holonomies}
\label{sec:maxwell}
% ===================================================================

\subsection{U(1) edge phases and discrete field strength}

Assign a U(1) phase to each oriented tangency edge:
\begin{equation}
  U_{ij}^{\rm EM}=e^{iqA_{ij}/\hbar},\qquad A_{ij}=-A_{ji}.
  \label{eq:edge_phase}
\end{equation}
The gauge-covariant graph derivative is
\begin{equation}
  (D_Af)_{ij}=U_{ij}^{\rm EM}f_j-f_i.
  \label{eq:cov_diff}
\end{equation}
The discrete field strength is the holonomy around an elementary graph cycle
$C=(i_1,i_2,\ldots,i_k,i_1)$:
\begin{equation}
  F_C=\arg\!\prod_{(ij)\in C}U_{ij}^{\rm EM}
  =\frac{q}{\hbar}\sum_{(ij)\in C}A_{ij}.
  \label{eq:holonomy}
\end{equation}
For a minimal three-tangency cycle, $F_C$ is the discrete analogue of magnetic
flux through the triangle.

\subsection{Discrete gauge action and Maxwell limit}

The candidate gauge-field action on the ASSP graph is
\begin{equation}
  S_A=-\frac14\sum_C W_C F_C^2+\sum_{(ij)}J_{ij}A_{ij},
  \label{eq:gauge_action}
\end{equation}
where $W_C$ are cycle weights set by the packing geometry. Stationarity
$\delta S_A/\delta A_{ij}=0$ gives a discrete divergence equation on the field
strength. The graph identity $d_G^2=0$ provides the discrete Bianchi identity
exactly. Under slow-variation and isotropy conditions, the cycle holonomies
expand to leading order in the gauge potential and the discrete divergence
maps to the continuum divergence, giving the candidate Maxwell limit
\begin{equation}
  \boxed{\partial_\mu F^{\mu\nu}=\mu_0J^\nu,\qquad
  \partial_{[\lambda}F_{\mu\nu]}=0.}
  \label{eq:maxwell}
\end{equation}
The normalization of $W_C$, the Lorentzian Hodge star, and the exact emergence
of $\mu_0$ are left as explicit tasks for the CLASSP gauge program.

\subsection{Coupling constant from register depth}

The electromagnetic coupling constant enters through the Presburger register
depth of one Soddy sphere~\cite{TFOFT2026,Soddy1936}:
\begin{equation}
  \alpha^{-1}=4\pi^3+\pi^2+\pi=137.036,\qquad
  \alpha=\frac{1}{T_{\rm sphere}}.
  \label{eq:alpha}
\end{equation}
Under the edge-phase ontology, $\alpha$ is the sequential-alignment probability
per quine cycle: the fraction of asynchronous two-ball register updates that
are causally ordered~\cite{TFOFT2026}. Higher-order tangency interactions are
conjectured to generate the gauge hierarchy toward $SU(2)$ and $SU(3)$.

% ===================================================================
\section{Simulation and Observation}
% ===================================================================

\subsection{Hydrogenic dark/inertial boundary fields}

In the TFOFT interpretation, dark matter is not primarily a particle species
but a lower-layer inertial boundary field~\cite{TFOFT2026}. The electron cloud
and the dark halo are both lower-layer boundary fields that constrain the
dynamics of the visible object (electron at atomic scale; stellar disk at
galactic scale). Therefore the simulation target is \emph{not}
\[
  \text{stars trace }|\psi_{nlm}|^2.
\]
The correct target is
\begin{equation}
  \mathcal{I}_{\rm halo}^{(nlm)}(R,z,\phi)
  \;\Longrightarrow\;
  \text{inertial/drag/clock field}
  \;\Longrightarrow\;
  \text{stellar disk response}.
  \label{eq:target}
\end{equation}
A minimal model uses hydrogenic orbital geometries as basis functions for the
dark/inertial field:
\begin{equation}
  \mathcal{I}(r,\theta,\phi)
  =\sum_{nlm}W_{nlm}
    \left|R_{nl}\!\left(\frac{r}{a_g}\right)Y_{lm}(\theta,\phi)\right|^2,
  \label{eq:inertia_basis}
\end{equation}
where $a_g$ is the galactic scale radius and $W_{nlm}$ are occupation weights.
A continuum observer may infer an effective density $\rho_{\rm eff}$ from
$\mathcal I$, but the physical object in the ASSP model is the inertial
boundary kernel rather than a literal cloud of particles.

The stellar disk evolves under
\begin{equation}
  \vec a_\star=-\nabla\Phi_{\rm baryon}-c^2\nabla u_{\rm halo}
  +\vec a_{\rm drag}[\mathcal I,\vec v]
  +\vec a_{\rm gyro}[\mathcal I,\vec v\times\hat n],
  \label{eq:disk_dynamics}
\end{equation}
where the first two terms are baryon and radius-clock gravity from
Eq.~\eqref{eq:poisson}, and the latter two represent the lower-layer inertial
drag and angular-momentum transfer channels responsible for flat-rotation
support. The M\"obius boundary acceleration~\eqref{eq:mobius_accel} provides
one analytic form for $\vec a_{\rm gyro}$.

For the $3d_{z^2}$ Milky Way state specifically, the effective inertial kernel
has the angular form
\begin{equation}
  \mathcal I_{3d_{z^2}}(r,\theta)
  =I_0\,\mathcal R_{32}(r/a_g)\,(3\cos^2\theta-1)^2,
  \label{eq:I_3dz2_general}
\end{equation}
where $\mathcal R_{32}$ is the scaled radial shell factor. If one uses the
hydrogenic density shape directly, then
\begin{equation}
  \mathcal R_{32}(r/a_g)
  \propto
  \left(\frac{r}{a_g}\right)^4
  \exp\!\left(-\frac{2r}{3a_g}\right).
  \label{eq:R32_shape}
\end{equation}
The scale $a_g$ is fixed by matching the polar Fermi-bubble height, not by
fitting the equatorial feature after the fact.

\subsection{Numerical simulation program}

The simulation comparison program is:
\begin{enumerate}[label=\textbf{S\arabic*.}]
  \item Build disk simulations with four halo/inertial models: NFW, Einasto,
        generic dark disk, and the hydrogenic ASSP inertial kernel
        $\mathcal I_{3d_{z^2}}$ from Eq.~\eqref{eq:I_3dz2_general}.
  \item Fit rotation curves, vertical force $K_z$, HI gas flaring, spiral
        structure, and stream perturbations.
  \item Ask whether a small set of hydrogenic orbital boundary states explains
        the same observables with fewer effective parameters.
  \item Allow transitions between boundary states,
        $\Psi_{\rm halo}(t)=\sum_{nlm}a_{nlm}(t)\psi_{nlm}$, and identify the
        disk and plasma response to $\Delta|\Psi_{\rm halo}|^2$.
\end{enumerate}

\subsection{The $3d_{z^2}$ Milky Way state and the Fermi bubbles}

The companion paper~\cite{TFOFT2026} identifies the Fermi
bubbles~\cite{FermiBubbles2010,Ackermann2014} as the polar lobes of a scaled
$3d_{z^2}$ boundary state. The angular factor is
\begin{equation}
  Y_{20}(\theta)\propto3\cos^2\theta-1.
  \label{eq:Y20}
\end{equation}
Its nodal cones lie at
\begin{equation}
  3\cos^2\theta-1=0
  \;\Longrightarrow\;
  \theta_{\rm node}=\arccos\frac{1}{\sqrt3}\approx54.74^\circ.
  \label{eq:nodal_angle}
\end{equation}
The Fermi bubbles extend roughly tens of degrees above and below the Galactic
center; the common descriptive scale is about $50\,\kly\approx15.3\,\kpc$, while
some modeling papers quote heights of order $10\,\kpc$ depending on the
geometric convention and distance model~\cite{FermiBubbles2010,Ackermann2014}.
We therefore define
\begin{equation}
  H_{\rm FB}\equiv\text{polar Fermi-bubble height}\sim10\text{--}15\,\kpc.
  \label{eq:HFB}
\end{equation}
This scale correction is crucial: $50\,\kly$ is not $50\,\kpc$.

The TFOFT rank fraction $(23/27)$ may be read as setting the polar-lobe height
relative to the full local halo/boundary scale,
\begin{equation}
  H_{\rm FB}=\frac{23}{27}R_{\rm halo}^{\rm local}.
  \label{eq:HFB_rank}
\end{equation}
Thus, for $H_{\rm FB}\sim10$--$15\,\kpc$,
\begin{equation}
  R_{\rm halo}^{\rm local}\sim\frac{27}{23}H_{\rm FB}\sim12\text{--}18\,\kpc.
  \label{eq:Rhalo_local}
\end{equation}
This places the associated equatorial component in the outer visible disk,
not in a remote $40$--$50\,\kpc$ halo annulus.

\subsection{The equatorial ``Fermi donut'': corrected derivation and prediction}

At the poles and at the equator, the squared $Y_{20}$ amplitude gives:
\begin{align}
  |Y_{20}|^2_{\rm pole}&\propto(3\cos^2 0-1)^2=(2)^2=4,
  \label{eq:pole}\\
  |Y_{20}|^2_{\rm equator}&\propto(3\cos^2(\pi/2)-1)^2=(-1)^2=1.
  \label{eq:equator}
\end{align}
Therefore
\begin{equation}
  \boxed{\frac{\mathcal I_{\rm equator}}{\mathcal I_{\rm pole}}
  =\frac{|Y_{20}|^2_{\rm equator}}{|Y_{20}|^2_{\rm pole}}=\frac14.}
  \label{eq:quarter_density}
\end{equation}
The same $3d_{z^2}$ state that produces the polar Fermi bubbles requires an
equatorial toroidal lobe of one-quarter the polar angular density contrast.
In the simplest same-radius shell interpretation, the torus peak is at the
same orbital scale as the polar lobe:
\begin{equation}
  R_{\rm donut,peak}\sim H_{\rm FB}\sim10\text{--}15\,\kpc.
  \label{eq:donut_peak_corrected}
\end{equation}
The torus does not possess a unique hard inner edge because an orbital density
surface depends on the chosen contour. For a fiducial shell/shoulder estimate,
using the nodal-cone geometry gives an inner shoulder of order
\begin{equation}
  R_{\rm donut,in}\sim\sqrt{\frac{2}{3}}\,H_{\rm FB}
  \approx0.816H_{\rm FB}
  \sim8\text{--}12\,\kpc.
  \label{eq:donut_inner_corrected}
\end{equation}
This places the predicted feature from approximately the solar circle and
outer disk into the region just beyond the main stellar disk scale. The
feature is therefore not a far-halo object; it is an outer-disk boundary
signature.

\begin{mdframed}
\textbf{Corrected prediction: Fermi donut.}
Using the real Fermi-bubble scale $H_{\rm FB}\sim10$--$15\,\kpc$, the Milky
Way $3d_{z^2}$ boundary state predicts an equatorial annular counterpart with:
\begin{itemize}
  \item fiducial inner shoulder $R_{\rm in}\sim8$--$12\,\kpc$;
  \item radial peak $R_{\rm peak}\sim10$--$15\,\kpc$;
  \item angular density/inertia contrast $\approx1/4$ of the polar lobes;
  \item geometry: a broad, low-contrast ring symmetric about the Galactic plane.
\end{itemize}
A coherent outer-disk boundary at this scale supports the $3d_{z^2}$ model.
A smooth featureless disk/halo through $R\sim8$--$20\,\kpc$ disfavors this
particular state identification.
\end{mdframed}

\subsection{Connection to Gaia DR3 outer-disk anomalies}

The corrected Fermi-donut scale overlaps the radial domain where recent Gaia
DR3 studies already report model-sensitive Milky Way dynamics. Sylos Labini
constructed generalized rotation curves from Gaia DR3 data over
$R=8.5$--$25\,\kpc$ and heights $z=-2$ to $+2\,\kpc$, comparing a canonical
NFW halo model with a dark-matter-disk (DMD) model in which the dark component
is confined to the Galactic plane and follows neutral hydrogen; that analysis
reported that the DMD model generally fits the large-radius on-plane and
off-plane behavior better than NFW~\cite{SylosLabini2024}. Other Gaia DR3
Jeans analyses find evidence for a declining rotation curve beyond
$\sim15\,\kpc$, while also warning that disequilibrium, non-axisymmetry, and
satellite perturbations can bias Jeans-inferred circular velocities at the
10--15\% level~\cite{Koop2024}. Earlier Gaia DR3 mapping extends disk
kinematic maps and rotation-curve reconstruction to roughly $30\,\kpc$,
providing exactly the radial coverage needed to search for the corrected
$3d_{z^2}$ equatorial boundary~\cite{Wang2023}.

This is not a claim that Gaia has already detected the Fermi donut. The point
is sharper: once the incorrect $50\,\kpc$ scale is removed, the TFOFT
prediction lands in the same $R\sim10$--$20\,\kpc$ outer-disk regime where
Gaia already indicates that simple spherical-halo modeling is under stress or
at least model-dependent. The $3d_{z^2}$ model predicts a specific angular and
radial boundary structure in that region, not merely a generic dark disk.

\subsection{Emission and star-formation scaling}

If the polar Fermi bubbles arise where the boundary state opens a high-density
angular channel, the equatorial torus produces weaker signatures for two
independent reasons: (1) the angular density is lower by
Eq.~\eqref{eq:quarter_density}; and (2) local baryonic plasma injection in the
outer disk differs from the central polar channel. If emissivity scales
linearly with boundary density and local star-formation/plasma production,
\begin{equation}
  I_{\rm donut}
  \sim\frac14
  \left(\frac{\Sigma_{\rm SFR}(R_{\rm donut})}{\Sigma_{\rm SFR,polar}}\right)
  I_{\rm bubble}.
  \label{eq:emission_linear}
\end{equation}
If the relevant emission is collisional or plasma-density squared,
\begin{equation}
  I_{\rm donut}
  \sim\frac{1}{16}
  \left(\frac{\Sigma_{\rm gas}(R_{\rm donut})}{\Sigma_{\rm gas,polar}}\right)^2
  I_{\rm bubble}.
  \label{eq:emission_quadratic}
\end{equation}
If the boundary operates by a threshold/ignition rule, the donut may appear
more strongly in dynamics, HI flaring, or stellar-stream perturbations than in
X-ray or gamma-ray brightness. Non-detection in all-sky emission maps is
therefore not decisive unless the search is tuned to the predicted low-contrast
outer-disk annulus.

\subsection{Observational program}

\begin{enumerate}[label=\textbf{O\arabic*.}]
  \item Search Gaia DR3-derived rotation and vertical-force residuals for a
        coherent boundary or slope change in $R\sim8$--$20\,\kpc$, especially
        near $R\sim10$--$15\,\kpc$.
  \item Compare the $3d_{z^2}$ inertial kernel against NFW, Einasto, and
        generic dark-disk models using the same Gaia DR3 generalized rotation
        curves and off-plane constraints.
  \item Search HI and outer-disk gas maps for flaring, compression, or ringlike
        behavior at the corrected donut scale.
  \item Search Fermi/eROSITA/radio residual maps for weak annular nonthermal
        emission in the Galactic plane at the predicted scale.
  \item Test whether stellar streams, open clusters, globular clusters, or
        satellite orbits show perturbations when crossing the predicted
        annular boundary.
\end{enumerate}

% ===================================================================
\section{Conclusion}
% ===================================================================

This paper gives the first continuum-limit skeleton of the TFOFT/ASSP ontology
of~\cite{TFOFT2026}. The primitive variable is the sphere radius; its logarithm
is the local clock field:
\begin{equation}
  u=\ln\frac{R}{R_0}.
\end{equation}
The radius-clock field obeys a graph Poisson equation that coarse-grains to
Newtonian gravity and to the weak-field $g_{00}$ sector of GR:
\begin{equation}
  \Delta_Gu=\frac{4\pi G}{c^2}\rho
  \;\Longrightarrow\;
  \nabla^2\Phi=4\pi G\rho,
  \qquad g_{00}=-c^2e^{2\Phi/c^2}.
\end{equation}
On the same graph, directed light-speed tangency walks with Gyro-Ball
chirality mixing coarse-grain to the Dirac equation~\cite{Ord1983,Dirac1928},
with the spin connection geometrically induced by inter-sphere frame rotation.
U(1) edge-phase holonomies provide a candidate graph route to Maxwell
electromagnetism.

GR and QM are not fundamental competitors in this ontology. They are effective
continuum shadows of a single finite fractal sphere-packing computation:
radius-clock gradients become gravity, directed tangency zigzags become
quantum matter, and edge-phase windings become gauge fields.

The immediate empirical test is galactic. Correcting the Fermi-bubble scale
from $50\,\kpc$ to $50\,\kly\approx15\,\kpc$ moves the predicted equatorial
$3d_{z^2}$ ``Fermi donut'' into the outer visible disk, with a fiducial inner
shoulder near $8$--$12\,\kpc$, a peak near $10$--$15\,\kpc$, and one-quarter
the polar-lobe angular density contrast. This is exactly the region where Gaia
DR3 rotation-curve and dark-disk analyses already show nontrivial,
model-sensitive behavior. The next step is to simulate spiral galaxies using
hydrogenic ASSP inertial kernels and to test the corrected $3d_{z^2}$ boundary
against Gaia, HI, stream, Fermi, eROSITA, and radio data before accepting the
full ontology.

\section*{Acknowledgments}
The author thanks the survey teams whose archival data will enable the
observational program of Section~6, and the mathematical physics community
whose work on Apollonian packings~\cite{Boyd1973,Graham2003}, graph
Laplacians, and Ord-style walks~\cite{Ord1983} provided the technical
scaffolding for the derivations above.

% ===================================================================
\begin{thebibliography}{99}

\bibitem{TFOFT2026}
S.~E. Elliott,
``The Fact of Fractal Tennis: The Universe as a Fractal Computer Defined by
the Star=Electron+Atom=Galaxy Quine,''
ai.vixra preprint 2605.0003, 2026.
\url{https://ai.vixra.org/abs/2605.0003}

\bibitem{Ord1983}
G.~N. Ord,
``Fractal space-time: a geometric analogue of relativistic quantum mechanics,''
\textit{J. Phys. A: Math. Gen.} \textbf{16}, 1869 (1983).

\bibitem{Soddy1936}
F.~Soddy,
``The Kiss Precise,''
\textit{Nature} \textbf{137}, 1021 (1936).

\bibitem{Boyd1973}
D.~W. Boyd,
``The residual set dimension of the Apollonian packing,''
\textit{Mathematika} \textbf{20}, 170 (1973).

\bibitem{Graham2003}
R.~L. Graham, J.~C. Lagarias, C.~L. Mallows, A.~R. Wilks, and C.~H. Yan,
``Apollonian circle packings: number theory,''
\textit{J. Number Theory} \textbf{100}, 1 (2003).

\bibitem{Mandelbrot1983}
B.~B. Mandelbrot,
\textit{The Fractal Geometry of Nature}
(W.~H. Freeman, 1983).

\bibitem{Presburger1929}
M.~Presburger,
``\"Uber die Vollst\"andigkeit eines gewissen Systems der Arithmetik ganzer
Zahlen,''
\textit{Comptes Rendus du I Congr\`es des Math\'ematiciens des Pays Slaves},
Warsaw, 1929, pp.~92--101.

\bibitem{Dirac1928}
P.~A.~M. Dirac,
``The quantum theory of the electron,''
\textit{Proc. R. Soc. A} \textbf{117}, 610 (1928).

\bibitem{FermiBubbles2010}
M.~Su, T.~R. Slatyer, and D.~P. Finkbeiner,
``Giant Gamma-ray Bubbles from Fermi-LAT: AGN Activity or Bipolar Galactic Wind?''
\textit{ApJ} \textbf{724}, 1044 (2010).

\bibitem{Ackermann2014}
M.~Ackermann et al.\ (Fermi-LAT Collaboration),
``The Spectrum and Morphology of the Fermi Bubbles,''
\textit{ApJ} \textbf{793}, 64 (2014).

\bibitem{Sarkar2015}
K.~C. Sarkar, B.~Nath, and P.~Sharma,
``On the origin of the Fermi bubbles,''
\textit{MNRAS} \textbf{453}, 3827 (2015).

\bibitem{Sofue2012}
Y.~Sofue,
``Rotation Curve and Mass Distribution in the Galactic Center,''
\textit{PASJ} \textbf{64}(4), 75 (2012).

\bibitem{Chemin2009}
L.~Chemin, C.~Carignan, and T.~Foster,
``Rotation Curve of the Andromeda Galaxy from Combined 21-cm Data,''
\textit{ApJ} \textbf{705}(2), 1395 (2009).

\bibitem{SylosLabini2024}
F.~Sylos Labini,
``Generalized rotation curves of the Milky Way from the GAIA DR3 data-set:
constraints on mass models,''
\textit{Astrophysical Journal} \textbf{976}, 185 (2024); arXiv:2410.14307.

\bibitem{Koop2024}
O.~Koop, T.~Antoja, A.~Helmi, T.~M.~Callingham, and C.~F.~P.~Laporte,
``On the Galactic rotation curve inferred from the Jeans equations: assessing
its robustness using Gaia DR3 and cosmological simulations,''
arXiv:2405.19028 (2024).

\bibitem{Wang2023}
H.-F. Wang, Z. Chrob\'akov\'a, M. L\'opez-Corredoira, and F. Sylos Labini,
``Mapping the Milky Way Disk with Gaia DR3: 3D Extended Kinematic Maps and
Rotation Curve to $\approx30$ kpc,''
\textit{Astrophysical Journal} \textbf{942}, 12 (2023).

\bibitem{Strassen1969}
V.~Strassen,
``Gaussian elimination is not optimal,''
\textit{Numer. Math.} \textbf{13}, 354 (1969).

\bibitem{CODATA2022}
E.~Tiesinga et al.,
``CODATA recommended values of the fundamental physical constants: 2022,''
\textit{Rev. Mod. Phys.} \textbf{96}, 025002 (2024).

\end{thebibliography}

\end{document}
